% =====================================================================
%  Master CV — Prakash Dhungana 
% =====================================================================
\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.58in,top=0.5in,bottom=0.45in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\pagestyle{empty}
\setlength{\parindent}{0pt}

% --- Section style: bold caps with rule -------------------------------
\titleformat{\section}{\large\bfseries}{}{0pt}{\uppercase}[\vspace{-6pt}\rule{\textwidth}{0.8pt}]
\titlespacing*{\section}{0pt}{7pt}{4pt}

% --- Tight bullets -----------------------------------------------------
\setlist[itemize]{leftmargin=14pt,itemsep=1pt,parsep=0pt,topsep=2pt,label=\textbullet}

\newcommand{\role}[4]{\vspace{3pt}{\textbf{#1}}\hfill{#4}\\{\itshape #2, #3}\vspace{1pt}}

\begin{document}

% ======================= HEADER =======================
\begin{center}
  {\LARGE\bfseries PRAKASH DHUNGANA}\\[3pt]
  Lexington, KY, USA \,|\, +1 859-806-9257 \,|\,
  \href{mailto:prakash.dhungana@uky.edu}{prakash.dhungana@uky.edu} \,|\,
  \href{https://linkedin.com/in/dhunganaprakas}{\underline{linkedin.com/in/dhunganaprakas}}
\end{center}

\section{Professional Summary}
Embedded software engineer with production experience delivering safety-critical C/C++ software for autonomous driving and in-vehicle systems across bare-metal, RTOS (QNX), and embedded Linux platforms. Integrated NVIDIA DriveOS Safety Services into a production automotive middleware stack under ISO~26262, built low-level PCIe/DMA drivers for deterministic multicore SoC communication, and configured AUTOSAR Basic Software with Vector DaVinci tooling. Ph.D. in Computer Engineering (Aug 2026) specializing in real-time optimization and TinyML for resource-constrained edge devices. Works fluently across the hardware-software boundary and within Agile teams, with deep debugging expertise (Lauterbach TRACE32, JTAG, GDB, logic analyzers) and a track record of peer-reviewed research.

\section{Core Competencies}
Embedded C/C++ \textbullet\ Kernel \& Device Driver Development (PCIe, DMA, Ethernet NIC, USB, MIPI camera) \textbullet\ Board Bring-up \& BSP \textbullet\ Bare-metal, RTOS (QNX), Embedded Linux (Yocto, Buildroot, systemd) \textbullet\ AUTOSAR Classic (MCAL, NvM, DEM, RTE; DaVinci) \textbullet\ ISO 26262 Functional Safety, MISRA-C/C++ \textbullet\ Vehicle Networks (CAN, Automotive Ethernet, SPI, I2C, UART) \textbullet\ Multi-threading, Concurrency \& Memory Management \textbullet\ TinyML / Edge AI \textbullet\ Debugging \& Profiling (TRACE32, JTAG, GDB, Logic Analyzers, VectorCAST) \textbullet\ Agile/Scrum, Jira, Confluence, Git/GitHub, CI/CD

\section{Professional Experience}

\role{Graduate Research Assistant -- Embedded AI \& Real-Time Systems}{University of Kentucky}{Lexington, KY, USA}{Jan 2023 -- Aug 2026}
\begin{itemize}
  \item Architected custom integer-only inference engines in C/C++ for ARM Cortex-M MCUs, eliminating floating-point overhead to minimize latency (41 ms) and memory footprint (13.5 kB).
  \item Interfaced bare-metal firmware with hardware to profile and optimize quantized ML execution on constrained edge devices, applying disciplined memory management under tight resource budgets.
  \item Developed feature extraction pipelines using wavelet packets and custom C/C++ kernels (14 ms feature extraction, 6 ms quantized inference); implemented on-device/federated continual learning for domain-shift robustness.
  \item Published peer-reviewed research and presented at international conferences; managed work using Git-based version control and iterative development.
\end{itemize}

\role{Embedded Software Engineer}{TTTech Auto (now TrustMotion)}{Osijek, Croatia}{Jul 2021 -- Dec 2022}
\begin{itemize}
  \item Integrated NVIDIA DriveOS Safety Services (3LSS) into the MotionWise autonomous-driving middleware platform, strictly adhering to ISO 26262 ASIL safety concepts and requirements.
  \item Implemented low-level C/C++ drivers for PCIe and DMA on multicore SoCs, enabling deterministic inter-processor communication between safety and performance hosts.
  \item Configured AUTOSAR Basic Software (MCAL, NvM, DEM) using Vector DaVinci Configurator and Generator, ensuring seamless integration with the Runtime Environment (RTE).
  \item Debugged complex system-level issues across middleware and low-level software using Lauterbach TRACE32, analyzing stack usage and intercore communication in an RTOS environment.
  \item Performed static analysis and unit testing with VectorCAST to MISRA-C/C++ standards; worked in an Agile/Scrum team, tracking tasks and defects in Jira and documenting designs in Confluence, with code managed via GitHub and CI/CD pipelines.
\end{itemize}

\role{Graduate Student Intern -- ADAS Embedded Software}{TTTech Auto (now TrustMotion)}{Osijek, Croatia}{Nov 2019 -- Jun 2021}
\begin{itemize}
  \item Optimized an automotive vision pipeline on TI TDA2x heterogeneous SoCs, reducing DSP execution time by 89.87\% through frame-wise lookup tables.
  \item Implemented C/C++ image-processing pipelines for panoramic image correction, meeting strict 60 fps real-time latency constraints on automotive hardware.
  \item Designed and validated a real-time panoramic image correction algorithm (color and brightness adjustment) on the ALPHA development board.
\end{itemize}

\role{Automotive Service Engineer}{IME Motors / Goldfish International}{Kathmandu, Nepal}{Dec 2016 -- Aug 2019}
\begin{itemize}
  \item Diagnosed complex faults in engines and vehicle subsystems using onboard diagnostic tools and Diagnostic Trouble Codes (DTCs).
  \item Analyzed electrical schematics and powertrain control module logic to resolve hardware-software interface issues in commercial vehicles.
\end{itemize}

\section{Key Projects}
\begin{itemize}
  \item \textbf{TinyML for Real-Time Audio Perception} (C/C++, Assembly) --- Integer-only signal-processing and classification pipeline for keyword spotting on MCUs; real-time quantized inference under strict latency/memory constraints; on-device continual learning. Peer-reviewed at ISQED 2024.
  \item \textbf{Panoramic Image Correction on ADAS Platform} (C++, DSP, RTOS) --- Brightness/color equalization algorithms implemented and validated on real automotive ADAS hardware for panoramic imaging.
\end{itemize}

\section{Education}
\textbf{Ph.D. in Computer Engineering}, University of Kentucky, Lexington, KY, USA \hfill 2023 -- 2026\\
\textbf{M.Sc. in Automotive Computing and Communications}, University of Osijek, Croatia \hfill 2019 -- 2021\\
\textbf{B.E. in Mechanical Engineering}, Tribhuvan University, Kathmandu, Nepal \hfill 2012 -- 2016

\section{Technical Skills}
\textbf{Programming Languages:} C, C++, Python, Bash, Assembly\\
\textbf{Operating Systems \& RTOS:} Embedded Linux, NVIDIA DriveOS, QNX, RTOS, Bare-metal\\
\textbf{Embedded Linux:} Buildroot, Yocto (OpenEmbedded), Cross-compilation Toolchains, Bootloaders, systemd\\
\textbf{Embedded Platforms:} NVIDIA Jetson \& Xavier, ARM Cortex-M/A, Aurix TriCore\\
\textbf{Driver \& Low-Level Development:} Kernel device driver development, PCIe, DMA, Ethernet NIC, USB, MIPI camera, FPGA interfaces, Board bring-up\\
\textbf{Systems Programming:} Multi-threading, Concurrency, Memory Management, System Architecture, Requirements Analysis, SDLC\\
\textbf{Communication Protocols:} CAN, Automotive Ethernet, TCP/IP, UDP, I2C, SPI, UART\\
\textbf{Testing \& Debugging:} TRACE32 (JTAG/Lauterbach), GDB, QNX Momentics, Logic Analyzers, Oscilloscopes, VectorCAST, Profiling, Unit/Integration/System-level testing\\
\textbf{Automotive Standards:} ISO 26262, AUTOSAR, ASPICE, MISRA\\
\textbf{SWE Practices \& Tools:} Agile/Scrum, Jira, Confluence, Git/GitHub, Bitbucket, CI/CD pipelines, Docker, Eclipse\\
\textbf{Embedded AI / TinyML:} TensorFlow Lite, Edge Inference, Integer-arithmetic Optimization, On-device Continual Learning\\
\textbf{Autonomy \& Robotics:} Real-time Control, Sensor/Actuator Integration, ADAS Perception Pipelines, Computer Vision

\section{Certifications}
Linux Device Drivers \& Kernel Programming \textbullet\ Automotive Software with AUTOSAR \& MotionWise \textbullet\ Advanced C++ Programming \textbullet\ Deep Learning A-Z (Neural Networks, TensorFlow) \textbullet\ The Complete Self-Driving Car Course - Applied Deep Learning

\end{document}
